NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/implementation.tex
finsih section 5 pass

%
The NLP model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
The visual elements are implemented in Javascript using \emph{D3.js} library , and the Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.

>>>>

%
In the proposed work, the NLI model is implemented in Python using \emph{pytorch}~\cite{PaszkeGrossChintala2017}.
The visual interface is implemented in Javascript using \emph{D3.js} library , and the Python server act as the glue between the Javascript visualization and the \emph{pytorch} model.

### 2018-03-31 paper/pipeline.tex
finsih section 5 pass

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{pipelineView}
 \vspace{-2mm}
 \caption{
The pipeline view provides the visual representation of the three-stage (encoder, attention, classifier) model. 
%
In the proposed tool, we allow model parameters to be updated to correct a prediction error. 
The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue rectangle marked with ``parameter'' to enable or disable its update (the legend is shown in (d)). In (c), we select whether we want to use the current pipeline setting as displayed or try all the pipeline configuration combinations as the parameter update operation can be enabled or disabled for each stage.
 }
\label{fig:pipelineView}
\vspace{-2mm}
\end{figure}

The optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a). Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with ``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ). In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current update setting as displayed or try all the configuration combinations (i.e., each stage can either be enabled or disabled for the three stages; therefore, there are $8$ combinations in total, or $7$ we discard the case where all stages are not updated).

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{pipelineView}
 \vspace{-2mm}
 \caption{
The pipeline view provides the visual representation of the three-stage (encoder, attention, classifier) model. 
%
In the proposed tool, we allow model parameters to be updated to correct a prediction error. 
The optimization hyperparameters are shown in (a), and each of the stages is illustrated in (b), where the user can click on the blue rectangle marked with the word ``parameter'' to enable or disable its update (the legend is shown in (d)). In (c), we select whether we want to use the current pipeline setting as displayed or try all the pipeline configuration combinations as the parameter update operation can be enabled or disabled for each stage.
 }
\label{fig:pipelineView}
\vspace{-2mm}
\end{figure}

The optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a). Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by clicking on the blue rectangle marked with the word``parameter'' (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d)). In Fig.~\ref{fig:pipelineView}(c), we select whether we want to use the current pipeline update setting as displayed or try all the pipeline configuration combinations (i.e., each stage can either be enabled or disabled; therefore, there are $8$ combinations in total, or $7$ if we discard the case where all stages are not enabled).

### 2018-03-31 paper/predSummary.tex
finsih section 5 pass

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \vspace{-6mm}
 \caption{
%Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) shows the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap to focus on the specific type of scenarios (e.g., E/E) and reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
The selection can be further narrowed down by selecting the bin in the histogram.
In (c) and (d), each point corresponds to one sentence pair.
 }
 \vspace{-2mm}
\label{fig:summaryView}
\end{figure}

@@

To address these challenges, we introduce the summary view (see Fig.~\ref{fig:teaser}(a)), which consists of a treemap, a histogram, and a scatterplot, to summarize the prediction results of the $10k$ examples and provide the ability to drill down to individual examples for detailed analysis.
%treemap for prediction
As illustrated in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the different combinations of the ground truth label and the predicted label. The green treemap blocks correspond to examples with correct predictions, whereas the orange blocks indicate failures. The size of the block encodes the number of examples belonging to each category.
%
By clicking on the treemap blocks, we can narrow down the selection by focusing on specific scenarios.
%
As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown. The histogram shows the distribution of the prediction sensitivity in the selected category. For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and the all the perturbed pairs. Considering we generated 100 pairs via the automated sentence perturbation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original prediction label. 
%The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
%
We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b),(d)).
%
In the scatterplot, besides showing the sensitivity value, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} number is likely to be quite noisy). %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \vspace{-6mm}
 \caption{
%Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) shows the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap node to focus on the specific type of scenarios (e.g., E/E) and reveal the histogram (b) and scatterplot (c) for displaying the selected subset.
The selection can be further narrowed down by selecting the bin in the histogram.
In (c) and (d), each point corresponds to one sentence pair.
 }
 \vspace{-2mm}
\label{fig:summaryView}
\end{figure}

@@

To address these challenges, we introduce the summary view (see Fig.~\ref{fig:teaser}(a)), which consists of a treemap, a histogram, and a scatterplot, to summarize the prediction results of the $10k$ examples and provide the ability to drill down to individual examples for detailed analysis.
%treemap for prediction
As illustrated in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the different combinations of the ground truth label and the predicted label. The green treemap blocks correspond to examples with correct predictions, whereas the orange blocks indicate failures. The size of the block encodes the number of examples belonging to each category.
%
By clicking on the treemap node, we can narrow down the selection by focusing on a specific scenario.

As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown. The histogram shows the distribution of the prediction stability in the selected category. For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and the all the perturbed pairs. Considering we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonymous), the stability is 0.8 if 80 out of the 100 maintain the original prediction label. 
%The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
%
We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b)).
%
In the scatterplot (Fig.~\ref{fig:summaryView}(c)(d)), besides showing the stability values, we also include the number of perturbed pairs (labeled as \emph{perturbCount}) to help users better assess the \emph{stability} number (i.e., if the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} value is likely very noisy). %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.
